---
title: "Data Mining - Association"
output:
  html_document:
    df_print: paged
---

## Data Loading and Preprocessing

First,we import in our Housing dataset and have a preliminary look at it.

```{r}
df = read.csv('austinHousingData.csv', header = TRUE)
head(df)
```

We need to get rid of the columns that we have not used in our database, followed by having a look at the datatype of the remaining columns

```{r}
df = subset(df, select = -c(description, numOfPhotos, latest_salemonth, latest_saleyear, homeImage))
colnames(df)
```

There are a few other variables that we do not require when performing data mining exercises. These includ, zpid, streetAddress, latitude, longitude, latestPriceSource.

```{r}
df = subset(df, select = -c(zpid, streetAddress, latitude, longitude, latestPriceSource))
sapply(df, typeof)
```

Firstly, all the columns with type 'character', except *homeType* and *latest_saledate*, are actually boolean values. So, we convert them into 0 & 1.
Also, we need to convert *latest_saledate* and *yearBuilt* columns to UNIX seconds so that they are better recognised by our model.

```{r}
df[,5:10][df[,5:10] == 'True'] = 1
df[,5:10][df[,5:10] == 'False'] = 0

df[,5:10] = sapply(df[,5:10], as.numeric)

df$latest_saledate = as.numeric ( as.POSIXct( 
  as.Date(df$latest_saledate, format = "%Y-%m-%d", origin = '1970-01-01') ) )
  
df$yearBuilt = as.numeric ( as.POSIXct(
  as.Date(df$yearBuilt, format = "%Y", origin = '1970-01-01') ) )
  
sapply(df, typeof)
```

Since all the column domains have such a difference in scale, we will normalize our data using `scale()` function.

```{r}
normdf = scale(subset(df, select = -c(city, homeType)))

normdf = data.frame(normdf)
head(normdf)
```

Now, for our last preprocessing step, we add the non-numeric columns to the normalized dataframe

```{r}
normdf$city = df$city
normdf$homeType = df$homeType

colnames(normdf)
```

Verifying once,
```{r}
setequal(colnames(df), colnames(normdf))
```
## Correlation

Let us have a look at Pearson's correlation coefficient matrix for our data. The funtion for it only accepts numeric data. We only print the coefficients for *latestPrice* column.
```{r}
corrmat <- cor( normdf[,-c(36,37)] )
round(corrmat[,'latestPrice'], 2)
```

## Model Building

```{r}
lrmodel = lm(latestPrice ~ ., data = normdf)
summary( lrmodel )
```


